On investigating heterogeneity in psychological phenomena

### 2024-04-09 ms.Rmd
Convert chunk options

```{r setup, include = FALSE}
# Packages
library(papaja)
library(janitor)
library(scales)
library(ellipse)
library(knitr)
library(cmdstanr)
library(readxl)
library(lme4)
library(ggpp)
library(patchwork)
library(latex2exp)
library(ggdist)
library(ggstance)
library(tidybayes)
library(distributional)
library(posterior)
library(parameters)
library(brms)
library(tidyverse)

@@

```{r data-bolgeretal, include = FALSE}
dir.create("data", FALSE)
# Load, save, & clean example data from Bolger et al. (2019)
path <- "data/bolger-etal.zip"
if (!file.exists(path)) {
  download.file(
    "https://github.com/kzee/heterogeneityproject/archive/refs/heads/master.zip",
    destfile = path
  )
  unzip(path, exdir = str_remove(path, ".zip"), junkpaths = TRUE)
}

@@

```{r fit1-lmer}
fit_lmer <- lmer(
  rt ~ 1 + valence + (1 + valence | person),
  data = dat
)
```

@@

```{r descriptors, include = FALSE}
# Heterogeneity interval
hi90_num <- qnorm(c(0.05, .95), mu1n, sd1n)
hi90 <- paste(
  number(hi90_num, .01),
  collapse = ", "
)
hi90_low <- paste(
  number(qnorm(c(0.05, .95), mu1n_low, sd1n_low), .01),
  collapse = ", "
)

@@

```{r fit1-brms}
fit_1 <- brm(
  rt ~ 1 + valence + (1 + valence | person),
  data = dat,
  file = "models/brm-fit-1",
  control = list(adapt_delta = .95)
)
```

@@

```{r data-mah-lindsay-3, include = FALSE}
# Experiment 3: task type is between-person
path <- "data/mah-lindsay-experiment-3.zip"
if (!file.exists(path)) {
  download.file(
    "https://files.ca-1.osf.io/v1/resources/pfhu9/providers/osfstorage/?zip=",
    destfile = path
  )
  unzip(path, exdir = str_remove(path, ".zip"), junkpaths = TRUE)
}

@@

```{r tab-dat2}
dat |>
  slice(4:6, .by = task) |> 
  apa_table(
    span_text_columns = FALSE,
    font_size = "small",
    escape = FALSE,
    digits = 0,
    caption = "Six rows of example dataset 2 (Mah \\& Lindsay, 2023; Exp 3)."
  )
```

@@

```{r fit-brms-ml3}
#| message: false

>>>>

```{r}
#| label = "setup",
#| include = FALSE
# Packages
library(papaja)
library(janitor)
library(scales)
library(ellipse)
library(knitr)
library(cmdstanr)
library(readxl)
library(lme4)
library(ggpp)
library(patchwork)
library(latex2exp)
library(ggdist)
library(ggstance)
library(tidybayes)
library(distributional)
library(posterior)
library(parameters)
library(brms)
library(tidyverse)

@@

```{r}
#| label = "data-bolgeretal",
#| include = FALSE
dir.create("data", FALSE)
# Load, save, & clean example data from Bolger et al. (2019)
path <- "data/bolger-etal.zip"
if (!file.exists(path)) {
  download.file(
    "https://github.com/kzee/heterogeneityproject/archive/refs/heads/master.zip",
    destfile = path
  )
  unzip(path, exdir = str_remove(path, ".zip"), junkpaths = TRUE)
}

@@

```{r}
#| label = "fit1-lmer"
fit_lmer <- lmer(
  rt ~ 1 + valence + (1 + valence | person),
  data = dat
)
```

@@

```{r}
#| label = "descriptors",
#| include = FALSE
# Heterogeneity interval
hi90_num <- qnorm(c(0.05, .95), mu1n, sd1n)
hi90 <- paste(
  number(hi90_num, .01),
  collapse = ", "
)
hi90_low <- paste(
  number(qnorm(c(0.05, .95), mu1n_low, sd1n_low), .01),
  collapse = ", "
)

@@

```{r}
#| label = "fit1-brms"
fit_1 <- brm(
  rt ~ 1 + valence + (1 + valence | person),
  data = dat,
  file = "models/brm-fit-1",
  control = list(adapt_delta = .95)
)
```

@@

```{r}
#| label = "data-mah-lindsay-3",
#| include = FALSE
# Experiment 3: task type is between-person
path <- "data/mah-lindsay-experiment-3.zip"
if (!file.exists(path)) {
  download.file(
    "https://files.ca-1.osf.io/v1/resources/pfhu9/providers/osfstorage/?zip=",
    destfile = path
  )
  unzip(path, exdir = str_remove(path, ".zip"), junkpaths = TRUE)
}

@@

```{r}
#| label = "tab-dat2"
dat |>
  slice(4:6, .by = task) |> 
  apa_table(
    span_text_columns = FALSE,
    font_size = "small",
    escape = FALSE,
    digits = 0,
    caption = "Six rows of example dataset 2 (Mah \\& Lindsay, 2023; Exp 3)."
  )
```

@@

```{r}
#| label = "fit-brms-ml3"
#| message: false
